### 2021-08-13 manuscript/supplementary.tex
Updated README. Re-compiled manuscript & supplementary materials.
Working additional features into plots and analyses.

\begin{figure}[H] \centering
\includegraphics[width=0.99\textwidth]{wordScores.pdf} \caption{The 40
  highest and lowest scoring words that are associated with
  bioinformatic benchmark articles from the training benchmark articles,
  compared to the background articles. The log-odds ratios (measured
  in bits) are indicated on the y-axis. }
\label{fig:wordScores} \end{figure}

@@

\section*{Data mining} % The \section*{} command stops section numbering

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures we expected to be
  predictive of software quality used in this study. These
are, reading from left to right, top to bottom: Accuracy -- the mean
normalised accuracy rank for each benchmarked method; Speed -- the
mean normalised speed rank for each benchmarked method;
JH5 -- the Journal H5 index to the highest impact journal that has published
a manuscript describing a method, data from GoogleScholar 2020 Metrics;
Cites -- the number of citations to the most cited manuscript describing a method, data from GoogleScholar;
H-index -- the H-index for the highest profile corresponding author from the
manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the
highest profile corresponding author from the manuscripts describing a method,
data from GoogleScholar User Profiles;
Relative ages for different tools, for each benchmark tools were ranked based upon publication dates, these ranks were normalised to lie between 0 and 1.
}
\label{fig:metricDistributions}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-distributions-permuted.pdf}
\caption{The distributions for the permuted accuracy and speed values, where accuracy and speed ranks have been normalised to lie between 0 and 1.
}
\label{fig:metricDistributionsPerm}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-pairs.pdf}
\caption{}
\label{fig:metricPairs}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{spearmanBarplot.pdf}
\includegraphics[width=0.45\textwidth]{spearmanBarplotSpeed.pdf}
\caption{The correlation between method accuracy (on the left) and
  method speed (on the right) and measures we expected to be
  predictive of software quality. E.g. author reputation measures
  (H-index, M-index), journal reputation (JH5 and JIF), number of
  users (citations and relative citations) or the recency of methods
  (year and relative age).  The correlations were estimated using
  Spearman's $\rho$. The signficant relationships are indicated with a
  ``*''. }
\label{fig:S2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Citation metrics and software tool speeds/accuracies.} Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
  3$ matrix. The shading indicates different median citation-based
  feature scores (redder shade indicates a higher value).  The shading
  indicate median H-indices ({\bf left}) and $log_{10}(citations)$
  ({\bf right}). }
\label{fig:heatmaps}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{commits-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{contributors-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Version control use and software tool speeds/accuracies.}
  Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
  3$ matrix. The shading indicates different median github-derived
  feature scores (redder shade indicates a higher value).  The shading
  indicate the number of commits ({\bf left}) and the number of code contributors
  ({\bf right}).
 }
\label{fig:heatmapsCommits}
\end{figure}

>>>>

\begin{figure}[H] \centering
\includegraphics[width=0.99\textwidth]{wordScores.pdf} \caption{The 40
  highest ({\bf right}) and lowest ({\bf left}) scoring words that are associated with
  bioinformatic benchmark articles from the training benchmark articles,
  compared to the background articles. The log-odds ratios (measured
  in bits) are indicated on the y-axis. }
\label{fig:wordScores} \end{figure}

@@

\section*{Data visualisations} % The \section*{} command stops section numbering

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures that have been proposed to be
predictive of software quality used in this study. These
are, reading from left to right, top to bottom:
Accuracy -- the mean normalised accuracy rank for each benchmarked method;
Speed -- the mean normalised speed rank for each benchmarked method;
JH5 -- the Journal H5 index to the highest impact journal that has published a manuscript describing a method, data from GoogleScholar 2020 Metrics;
Cites -- the number of citations to the most cited manuscript describing a method, data from GoogleScholar;
H-index -- the H-index for the highest profile corresponding author from the manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the highest profile corresponding author from the manuscripts describing a method, data from GoogleScholar User Profiles;
Relative ages -- for different tools, for each benchmark tools were ranked based upon publication dates, these ranks were normalised to lie between 0 and 1.
Relative \#citations -- within each benchmark, what is the relative age of each tool, this corrects for older research fields (e.g. sequence alignment) vs newer research fields (e.g. single-cell sequencing);
Year published -- the first year each software tool was published;
Version -- the most resent version number for each tool;
Commits -- the number of commits to Github;
Contributors -- the number of contributors to a Github repository;
\#Issues -- the number of open and closed issues for each Github repository;
\%Open issues -- the pecentage of issues that remain open for each Github repository;
\#Pull requests -- the number of pull requests to a Github repository;
\#Forks -- the number of times a Github repository has been forked;
}
\label{fig:metricDistributions}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-distributions-permuted.pdf}
\caption{The distributions for the permuted accuracy ({\bf left}) and speed ({\bf right}) values, where accuracy and speed ranks have been normalised to lie between 0 and 1.
}
\label{fig:metricDistributionsPerm}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-pairs.pdf}
\caption{Dot plots for each feature relative to every other feature
  (accuracy, speed, JH5, citations, H-index, M-index, relAge,
  relCites, yearPublished, version, commits, contributors,
  ).

}
\label{fig:metricPairs}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{spearmanBarplot.pdf}
\includegraphics[width=0.45\textwidth]{spearmanBarplotSpeed.pdf}
\caption{The correlation between method accuracy ({\bf left}) and
  method speed ({\bf right}) and measures we expected to be
  predictive of software quality. E.g. author reputation measures
  (H-index, M-index), journal reputation (JH5 and JIF), number of
  users (citations and relative citations) or the recency of methods
  (year and relative age).  The correlations were estimated using
  Spearman's $\rho$. The signficant relationships are indicated with a
  ``*''. }
\label{fig:S2}
\end{figure}

@@

%% \begin{figure}[H]
%% \centering
%% \includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
%% \includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
%% \caption{{\bf Citation metrics and software tool speeds/accuracies.} Heatmaps of normalised speed ranks and normalised accuracy
%%   ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
%%   3$ matrix. The shading indicates different median citation-based
%%   feature scores (redder shade indicates a higher value).  The shading
%%   indicate median H-indices ({\bf left}) and $log_{10}(citations)$
%%   ({\bf right}). }
%% \label{fig:heatmaps}
%% \end{figure}

@@

%% \begin{figure}[H]
%% \centering
%% \includegraphics[width=0.45\textwidth]{commits-SpeedVsAccuracy-heatmap.pdf}
%% \includegraphics[width=0.45\textwidth]{contributors-SpeedVsAccuracy-heatmap.pdf}
%% \caption{{\bf Version control use and software tool speeds/accuracies.}
%%   Heatmaps of normalised speed ranks and normalised accuracy
%%   ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
%%   3$ matrix. The shading indicates different median github-derived
%%   feature scores (redder shade indicates a higher value).  The shading
%%   indicate the number of commits ({\bf left}) and the number of code contributors
%%   ({\bf right}).
%%  }
%% \label{fig:heatmapsCommits}
%% \end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.99\textwidth]{numberBenchmarksPerToolBarplot.pdf}\\
\includegraphics[width=0.99\textwidth]{numberRealValueFeaturesBarplot.pdf}
\caption{ {\bf Top:} The number of benchmarks each software tool has appeared in. {\bf Bottom:}
  Plot of the amount missing/known data for each of the software features used in this analysis. 
 }
\label{fig:numBenchmarks}
\end{figure}
